Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-13 paper/disc20clustering.tex
Title

 \usepackage{balance}
 \usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
 \usepackage{comment}
 \usepackage{balance}
 \usepackage{tikz}
 \usepackage{amsmath}
 \usetikzlibrary{patterns} %
 \usepackage{algorithm}
 \usepackage[font={footnotesize}]{subcaption}
 \usepackage[font={footnotesize}]{caption}
 \usepackage{breakcites}
 \usepackage{booktabs}
 \usepackage{diagbox}
 \usepackage{xcolor}
 \usepackage{colortbl}
 \usepackage{cleveref}
 \usepackage{enumitem}

@@

 \title{Tight Bounds for Dynamic Balanced Graph Partitioning}

@@

% \EventEditors{}
%\EventNoEds{3}
 \EventLongTitle{34th International Symposium on DIStributed Computing (DISC) 2020)}
 \EventShortTitle{DISC 2020}
 \EventAcronym{DISC}
 \EventYear{2020}
 \EventDate{October 12--16, 2020}
 \EventLocation{Freiburg, Germany (virtual conference)}
 \EventLogo{}
 \SeriesVolume{}
 \ArticleNo{}

>>>>

 \usepackage{balance}
 \usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
 \usepackage{comment}
 \usepackage{balance}
 \usepackage{tikz}
 \usepackage{amsmath}
 \usetikzlibrary{patterns} %
 \usepackage{algorithm}
 \usepackage[font={footnotesize}]{subcaption}
 \usepackage[font={footnotesize}]{caption}https://www.wykop.pl/
 \usepackage{breakcites}
 \usepackage{booktabs}
 \usepackage{diagbox}
 \usepackage{xcolor}
 \usepackage{colortbl}
 \usepackage{cleveref}
 \usepackage{enumitem}

@@

 \title{Optimal Algorithms for Dynamic Balanced Graph Partitioning}

@@

% \EventEditors{}
%\EventNoEds{3}
 \EventLongTitle{34th International Symposium on DIStributed Computing (DISC) 2020}
 \EventShortTitle{DISC 2020}
 \EventAcronym{DISC}
 \EventYear{2020}
 \EventDate{October 12--16, 2020}
 \EventLocation{Freiburg, Germany (virtual conference)}
 \EventLogo{}
 \SeriesVolume{}
 \ArticleNo{}
